First Order Alternation

### 2017-05-22 quantifiers/draft.tex
ok

Given sets of variables $B,X \subset \vars$ of sort $\Bool$ and
$\Data$, respectively, we denote by $\Form(B,X,Y)$ the set of formulae
$\phi$ such that $\fv{\Bool}{\phi} = B$, $\fv{\Data}{\phi} = X$ and
each variable from $Y$ is of sort $\Data$ and occurs under the scope
of a quantifier. By $\Form^+(B,X,Y)$ we denote the subset of
$\Form(B,X,Y)$ in which each boolean variable occurs under an even
number of negations.

@@

>>>>

Given sets of variables $B,X \subset \vars$ of sort $\Bool$ and
$\Data$, respectively, we denote by $\Form(B,X,Y)$ the set of formulae
$\phi$ such that $\fv{\Bool}{\phi} = B$, $\fv{\Data}{\phi} = X$ and
each variable from $Y$ is of sort $\Data$ and occurs under the scope
of a quantifier. By $\Form^+(B,X,Y)$ we denote the subset of
$\Form(B,X,Y)$ in which each boolean variable occurs under an even
number of negations. We denote by $\phi(B,X,Y)$ any formula from
$\Form(B,X,Y)$.

@@

In order to define the semantics of automata, we consider time-stamped
sets of variables $\stamp{X}{n} = \{\stamp{x}{n} \mid x \in X\}$ for
any $n\geq0$. For an input event $a \in \Sigma$, some constant
$n\geq0$ and a formula $\phi$, we write $\stamp{\Delta}{n}(\phi,a)$
for the formula obtained from $\phi$ by simultaneously replacing each
state $q \in \fv{\Bool}{\phi}$ with
$\Delta(\phi,a)[\stamp{G}{n}/\overline{G}, \stamp{G}{n+1}/G,
  \stamp{L}{n}/\overline{L}, \stamp{L}{n+1}/L]$.

Given a word $w = (a_1,\nu_1)(a_2,\nu_2) \ldots (a_n,\nu_n) \in
\Sigma[G]^*$ the \emph{run} of $\A$ over $w$ is the sequence of
formulae: \[\phi_0 \Rightarrow \phi_1(Q,\stamp{G}{0} \cup \stamp{G}{1},
\stamp{L}{0} \cup \stamp{L}{1}) \Rightarrow \ldots \Rightarrow
\phi_n(Q,\stamp{G}{0} \cup \ldots \cup \stamp{G}{n}, \stamp{L}{0} \cup
\ldots \cup \stamp{L}{n})\]
where: \begin{compactitem}
\item $\phi_0 \equiv \iota$, 
%
\item $\phi_1 \equiv \exists \stamp{L}{0} ~.~ \stamp{\Delta}{0}(\iota,a_1)$, and
%
\item $\phi_{i+1} \equiv \stamp{\Delta}{i}(\phi_i,a_{i+1})$, for all $i \in [1,n-1]$.
\end{compactitem}
We say that $\A$ \emph{accepts} $w$ if $\I,\nu \models
\phi_n(Q,\stamp{G}{0} \cup \ldots \cup \stamp{G}{n}, \stamp{L}{0} \cup
\ldots \cup \stamp{L}{n})$, where $\nu$ is a valuation such
that: \begin{compactitem}
\item $\nu(\stamp{g}{i}) = \nu_i(g)$ for each $g \in G$, 
%
\item $\nu(q) = \true$ for each $q \in F$, and
%
\item $\nu(q) = \false$ for each $q \in Q \setminus F$.
\end{compactitem}
The language of $\A$ is the set $L(\A)$ of words from $\Sigma[G]^*$
accepted by $\A$. In the following, we ask two
questions: \begin{compactenum}
\item given automata $\A_i = \tuple{G,L_i,Q_i,\iota_i,F_i,\Delta_i}$,
  with $L_1 \cap L_2 = \emptyset$ and $Q_1 \cap Q_2 = \emptyset$, do
  there exist automata $\A_\cap$, $\A_\cup$ and $\overline{\A}_1$ such
  that $L(\A_\cap) = L(\A_1) \cap L(\A_2)$, $L(\A_\cup) = L(\A_1) \cup
  L(\A_2)$ and $L(\overline{\A}_1) = \Sigma[G]^* \setminus L(\A_1)$ ?
%
\item given an automaton $\A$, is $L(\A) = \emptyset$ ? 
\end{compactenum}
